Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-10-11 manuscript.Rmd
fix typo

One widely known factor is the contribution of statistical methods to theoretical risk.
Theoretical risk $P(\neg{}E|\neg{}H)$ is deeply connected with statistical methods, because it is related to the type-I error rate in statistical hypothesis testing $P(E|\neg{}H)$ by $P(\neg{}E|\neg{}H) = 1 - P(E|\neg{}H)$, if you consider the overly simplistic case where the research hypothesis is equal to the statistical alternative-hypothesis because then the nill-hypothesis is $\neg{}H$.
Because many researchers are familiar with the type-I error rate, it can be helpful to remember this connection to theoretical risk.
Researchers who choose a smaller type-I error rate can be more sure of their results, if significant, because the theoretical risk is higher.
However, this connection should not be overinterpreted for two reasons.
First, according to most interpretations of null hypothesis testing, the absence of a significant result should not generally be interpreted as evidence against the hypothesis [@mayoStatisticalInferenceSevere2018, 5.3].
Second, the research hypothesis seldomly equals the statistical alternative-hypothesis (most research hypothesis are more specific then any value except zero).
In fact, it is entirely possible to assume the null hypothesis as a research hypothesis, as is commonly done in e.g., structural equation modelling, where the roles of detectability, theortical risk and type-I/II error rate switch.
We argue that theoretical risk (and hence its complement, $P(E|\neg{}H)$) also encompasses factors outside the statistical realm, most notably the study design and broader analytical strategies.
Type-I error rate is the property of a statistical test under some assumptions, whereas theoretical risk is a researchers believe.
One may take such theoretical properties as a first starting point to form a substantive believe but surely researchers ought to take more factors into consideration.
For example, if a researcher believes that there might be confounding variables at play for the relation between two variables, that should decrease the theorethical risk; after all they might find an association purely on account of the confounders.

>>>>

One widely known factor is the contribution of statistical methods to theoretical risk.
Theoretical risk $P(\neg{}E|\neg{}H)$ is deeply connected with statistical methods, because it is related to the type-I error rate in statistical hypothesis testing $P(E|\neg{}H)$ by $P(\neg{}E|\neg{}H) = 1 - P(E|\neg{}H)$, if you consider the overly simplistic case where the research hypothesis is equal to the statistical alternative-hypothesis because then the nill-hypothesis is $\neg{}H$.
Because many researchers are familiar with the type-I error rate, it can be helpful to remember this connection to theoretical risk.
Researchers who choose a smaller type-I error rate can be more sure of their results, if significant, because the theoretical risk is higher.
However, this connection should not be overinterpreted for two reasons.
First, according to most interpretations of null hypothesis testing, the absence of a significant result should not generally be interpreted as evidence against the hypothesis [@mayoStatisticalInferenceSevere2018, 5.3].
Second, the research hypothesis seldomly equals the statistical alternative-hypothesis (most research hypothesis are more specific then any value except zero).
In fact, it is entirely possible to assume the null hypothesis as a research hypothesis, as is commonly done in e.g., structural equation modelling, where the roles of detectability, theoretical risk and type-I/II error rate switch.
We argue that theoretical risk (and hence its complement, $P(E|\neg{}H)$) also encompasses factors outside the statistical realm, most notably the study design and broader analytical strategies.
Type-I error rate is the property of a statistical test under some assumptions, whereas theoretical risk is a researchers believe.
One may take such theoretical properties as a first starting point to form a substantive believe but surely researchers ought to take more factors into consideration.
For example, if a researcher believes that there might be confounding variables at play for the relation between two variables, that should decrease the theorethical risk; after all they might find an association purely on account of the confounders.
